\documentclass[11pt]{article}

%%%%%%%%%%%%%%%%%%%%
%% Document Setup %%
%%%%%%%%%%%%%%%%%%%%
\usepackage[paper=letterpaper,top=1in, bottom=1in, right=1in, left=1in]{geometry}
\setlength{\parindent}{0mm}
\usepackage{fix-cm}
\hyphenpenalty=1000000 % no auto-hypenation
\usepackage{hyperref}
%%%%%%%%%%%%
%% Tables %%
%%%%%%%%%%%%
\usepackage{array}
\usepackage{bigstrut}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{tabularx}

%%%%%%%%%%%%%
%% Columns %%
%%%%%%%%%%%%%
\usepackage{multicol}

%%%%%%%%%%%%%%%%%%%%%%%
%% Template Commands %%
%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\bigname}[3]{{\fontsize{#2}{#3}\selectfont #1}}
\newcommand{\phyaddress}[3]{{\fontsize{#2}{#3}\selectfont #1}}
\newcommand{\ncheader}[9]{
  \newlength{\oldtabcolsep}
  \setlength{\oldtabcolsep}{\tabcolsep}
  \setlength{\tabcolsep}{2.0em}
  \newlength{\oldbigstrutjot}
  \setlength{\oldbigstrutjot}{\bigstrutjot}
  \setlength{\bigstrutjot}{4pt}
  \begin{tabularx}{\textwidth}{@{}X p{#3}@{}}
    \multirow{2}[2]{*}[#4]{\centering\mbox{#1}} &
    \makebox[\linewidth][s]{\fontsize{#8}{#9}\selectfont
      \textrm{\mbox{#5} \mbox{#6}}} \bigstrut[t] \bigstrut[t] \\
    & \makebox[\linewidth][s]{\fontsize{#8}{#9}\selectfont
      \textrm{\mbox{#2} \mbox{#7}}} \bigstrut[t] \bigstrut[t] \\
    &
  \end{tabularx}
  \setlength{\bigstrutjot}{\oldbigstrutjot}
  \setlength{\tabcolsep}{\oldtabcolsep}
  \let\oldtabcolsep\undefined
}

\newcommand{\secheader}[1]{

  {\begin{tabularx}{\textwidth}{@{}X}
    \midrule[0.095em] \\ \addlinespace[-1.2em]
     \uppercase{\large{#1}} \\
    %\bottomrule[0.02em]
  \end{tabularx}\hfill\\\\}
}

\newcommand{\itemplaceheader}[2]{
  {\begin{tabular*}{\textwidth}{%
        @{\extracolsep{\fill}}%
        @{}l@{}%
        @{}r@{}}
      \textbf{#1} & {#2}
  \end{tabular*}}
}

\newcommand{\itempositionheader}[2]{
  {\setlength{\tabcolsep}{0em}
    \begin{tabular*}{\textwidth}{%
        @{\extracolsep{\fill}}
        @{}l@{}%
        @{}r@{}}
      \textrm{#1} & \textrm{#2}
  \end{tabular*}}
}

\begin{document}
% \ncheader{\bigname{Ram Raghunathan}{38}{39}}
%          {Pittsburgh, PA}
%          {6cm}
%          {0mm}
%          {ram.r@cs.cmu.edu}
%          {}
%          {}
%          {18}
%          {19}

\begin{center}
  \bigname{Janani Kalyanam}{25}{25} \\[0.75em]
  jkalyana@ucsd.edu OR janani.kalyanam@gmail.com \\
    Work Permit:  US Citizen \\
    Website: \url{acsweb.ucsd.edu/~jkalyana}
\end{center}
\secheader{Summary}
\small{I build machine learning based tools to extract useful information from social media
which is inherently unstructured and noisy.  I develop innovative unsupervised methods
that can accommodate for the unstructured nature in the data,
and combat the noise efficiently.  I have used these methods predominantly on Twitter data to (1) discover trends of drug abuse,
(2) identify illicit online pharmacies, and (3) identify high-impact news events at the
early stages of their outbreak.}
\secheader{Education}
\itemplaceheader{University of California, San Diego}{La Jolla, CA}
\itempositionheader {Ph.D. in Electrical and Computer Engineering} {Expected Spring 2017}
Advisor: Professor Gert Lanckriet\\  
Research keywords: social networks, machine learning, data science, unsupervised learning, NLP\\

\itemplaceheader{University of Wisconsin}{Madison, WI}
\itempositionheader {M.S. in Electrical and Computer Engineering} {2009}
%Thesis: ``Probabilistic Algorithm for List Viterbi Decoding''\\
%Advisor: Professor Stark Draper \\

\itemplaceheader{Rutgers University}{New Brunswick, NJ}
\itempositionheader {B.S. in Electrical and Computer Engineering} {2007}
%James. J. Slades Scholar for academic excellence \\
%Dean's List, all semesters \\

\secheader{Relevant Courses}
Statistical Learning, Convex Optimization, Parameter Estimation, Manifold Learning, Kernel Methods\\

\secheader{Skills}
Languages: C, C++, Java, Python, Matlab, LaTeX \\
Operating System: Linux, Windows, MAC \\

\secheader{Publications}
\textbf{Janani Kalyanam}, Mauricio Quezada, Barbara Poblete and Gert Lanckriet (2016). 
``Prediction and Characterization of High-Activity Events in Social Media Triggered by Real-World News''
\textit{PLOS ONE} \\

\textbf{Janani Kalyanam}, Takeo Katsuki, Gert Lanckriet and Tim Mackey (2016).
``Exploring Trends of Nonmedical use of Prescription Drugs and Polydrug Abuse in the Twittersphere Using Unsupervised Machine Learning''
\textit{Addictive Behaviors} \\

\textbf{Janani Kalyanam}, Sumithra Velupillai, Mike Conway and Gert Lanckriet (2016).
``From Event Detection to Story Telling on Microblogs''
\textit{Proceedings of the ACM/IEEE Conference on Advances in Social Network Analysis and Mining (ASONAM)} \\

\textbf{Janani Kalyanam}, Amin Mantrach, Diego Saez-Trumper, Hossein Vahabi and Gert Lanckriet (2015). 
``Leveraging Social Context for Modeling Topic Evolution.''
\textit{Proceedings of the 21st International Conference on Knowledge Discovery and Data Mining (KDD).} \\

\textbf{Janani Kalyanam}, Sumithra Velupillai, Son Doan, Mike Conway and
Gert Lanckriet (2015). ``Facts and Fabrications about Ebola:  A Twitter
Based Study'' \textit{SIGKDD Workshop on Connected Health in Big Data Era.} \\
\textbf{Best Paper Award.}\\

\textbf{Janani Kalyanam} and Gert Lanckriet (2014). 
``Learning from Unstructured Multimedia Data.'' \textit{Proceedings of the
23rd International Conference on World Wide Web (WWW).} \\

Andrew Bolstad, Benjamin Miller, Joel Goodman and \textbf{Janani Kalyanam} (2011). 
``Identification and Compensation of Wiener Hammerstein Systems with Feedback.'' 
\textit{Proceedings of the 36th International Conference on Accoustics, Speech and
Signal Processing.} \\

Joel Goodman, Benjamin Miller, Andrew Bolstad, Jim Vian and \textbf{Janani Kalyanam} (2011). 
``Physical Layer Considerations for Wideband Cognitive Radio.''
\textit{Military Communications Conference, 2011.} \\

\textbf{Janani Kalyanam.}  (2009).
``Probabilistic Algorithm for List-Viterbi Decoding.''
\textit{Masters Thesis.} \\

Chandrasekharan Raman, \textbf{Janani Kalyanam}, Ivan Seskar and Narayan Mandayam (2007).
``Distributed Spatio Temporal Spectrum Sensing:  An Experimental Study.''
\textit{Asilomar Conference on Signals, Systems and Computers.} \\

\secheader{Work Experience}
\itemplaceheader{University of California, San Diego}{La Jolla, CA}
\itempositionheader{Teaching Assistant}{}
Served as TA for programming courses at UCSD several times.\\ 
\hfill \\
\itemplaceheader{NEC Labs}{Princeton, NJ}
\itempositionheader{Research Intern}{2016}
Worked on mining non-linear dependencies via neighborhood mixtures \\ 
\hfill \\
\itemplaceheader{Massachusetts Institute of Technology - Lincoln Labs}{Lexinton, MA}
\itempositionheader{Intern}{2009}
Worked on calibrating power amplifiers. \\ 
\hfill \\
\itemplaceheader{Merrill Lynch}{Pennington, NJ}
\itempositionheader{Intern}{2006, 2007}
Web developer, Testing for IVRs \\

\secheader{Miscellaneous}
Completed the La Jolla Half Marathon (2013), Southern California Half Marathon (2014), and
the Girls on the Go Run Half Marathon (2014).

\end{document}

% Local Variables:
% coding: utf-8
% mode: latex
% TeX-engine: xetex
% TeX-master: t
% End:
